Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-01-28 paper/compilation.tex
more edits

The front-end (FE) of \sysname simplifies operators' task of describing preferred paths. That simplicity, however, comes at the cost of compilation complexity. The compiler must efficiently compute the sets of paths represented by the intersection of preferences and topology, compute which ones can be honored under failures, and ensure policy compliance under all possible failure cases.

%\subsection{Overview}

@@

%In this section we briefly describe our compilation strategy for \sysname.

@@

\para{Syntax}
The \sysname FE is just a thin layer atop a core, regular-expression language for describing preference-based path constraints. 
Figure~\ref{fig:rir-syntax} shows the RIR syntax. A policy consists of one or more constraints, each of which consists of a test on the type of route, and a corresponding set of preferred regular paths. Regular paths are regular expressions where the base characters are abstract locations---either a router or an AS. Special \In{} and \Out{} symbols refer to any internal or external location respectively.  In addition, $\Sigma$ refers to any symbol, and hence $\Sigma^*$ is
any sequence of symbols.  We also use other standard abbreviations
for regular expressions such as $r^+$, a sequence of one or more occurrences
of $r$, when appropriate.
%% For example, the constraint
%% \[(\textit{prefix}=74.3.28.0/24) \Link \\
%% (as200 \cdot \In^+) \Prefer (as100 \cdot \In^+)
%% \]
%% describes a more-preferred set of paths for traffic announced by a prefix no less specific than \CD{74.125.28.0/24}, which starts at AS 200, before entering and staying inside the user's network to get to the destination, and a less-preferred set of paths that start at AS 100 and are otherwise the same. The plus operator $\In^+$ stands for $\In \cdot \In^*$, at least one internal hop. Tests over route types use standard boolean connectives, and can refer to both prefixes and route community values.

>>>>

The front-end (FE) of \sysname simplifies operators' task of describing preferred paths. That simplicity, however, comes at the cost of compilation complexity. The compiler must efficiently compute the sets of paths represented by the intersection of preferences and topology, determine which ones can be honored under failures, and ensure policy compliance under all possible failure cases.

@@

@@

\para{Syntax}
The \sysname FE is just a thin layer atop a core, regular-expression language (RIR) for describing preference-based path constraints. 
Figure~\ref{fig:rir-syntax} shows the RIR syntax. A policy consists of one or more constraints, each of which consists of a test on the type of route, and a corresponding set of preferred regular paths. Regular paths are regular expressions where the base characters are abstract locations---either a router or an AS. Special \In{} and \Out{} symbols refer to any internal or external location respectively.  In addition, $\Sigma$ refers to any symbol, and hence $\Sigma^*$ is
any sequence of symbols.  We also use other standard abbreviations
for regular expressions such as $r^+$, a sequence of one or more occurrences
of $r$, when appropriate.
%% For example, the constraint
%% \[(\textit{prefix}=74.3.28.0/24) \Link \\
%% (as200 \cdot \In^+) \Prefer (as100 \cdot \In^+)
%% \]
%% describes a more-preferred set of paths for traffic announced by a prefix no less specific than \CD{74.125.28.0/24}, which starts at AS 200, before entering and staying inside the user's network to get to the destination, and a less-preferred set of paths that start at AS 100 and are otherwise the same. The plus operator $\In^+$ stands for $\In \cdot \In^*$, at least one internal hop. Tests over route types use standard boolean connectives, and can refer to both prefixes and route community values.

### 2016-01-28 paper/motivation.tex
more edits

 While configuring policies for a fully functional network is difficult, ensuring policy compliance in the face of failures can be almost impossible. Consider the data center network in Figure~\ref{fig:example2} with routers organized as a fat tree and running BGP.\footnote{For scale and policy flexibility, data center networks increasingly use BGP internally, with a private AS number per router~\cite{bgp-in-dc}.} The network has two clusters, one with services that should be reachable globally and one with services that should be accessible only internally. This policy is enabled by using non-overlapping address space in the two clusters and ensuring that only the address space for the global services is announced externally. Further, to reduce the number of prefixes that are announced externally, the global space is aggregated into a less-specific prefix $P_G$. The semantics of aggregation is that the aggregate prefix is announced as long as the router has a path to at least one sub-prefix.

The operator may decide that a simple way to implement the policy is to have X and Y: $i)$ not export externally what they hear from G and H, routers that belong to the local services cluster; and $ii)$ announce what they hear from routers C and D and aggregate to $P_G$ if an announcement is subset of $P_G$. This implementation is appealing because X and Y do not need to be made aware of which prefixes are global versus local and IP address assignment can be done independently (e.g., new prefixes can be assigned to local services without updating router configurations).

However, this implementation does not have the right behavior in the face of failures. Suppose links X--G and X--H fail. Then, X will hear announcements for $P_{l*}$ from C and D, having traversed from G and H to Y to C and D. Per policy implementation, X will start "leaking" these prefixes externally. Depending on the rationale for local services, this leak could impact security (e.g., if the services were sensitive) or availability (e.g., if the $P_{l*}$ prefixes are used for other services outside of the data center). This problem does not manifest without failures because then X has and prefers paths to $P_{l*}$ through G and H since they are shorter. A similar problem will happen if links Y--G and Y--H fail.
%\footnote{A different problem occurs when links X--C and X--D (or Y--C and Y--D) fail. X (Y) may stop announcing the global prefixes because they would be heard through G and H.}
Link failures in data centers are frequent and it is not uncommon to have multiple failed links at a given time~\cite{dc-failure-study}.

To avoid this problem, the operator may decide to disallow "valleys" paths, i.e., those that go up, down, and back up again. This guard can be implemented by $X$ and $Y$ rejecting paths through the other. But that creates a different problem in the face of failures---an aggregation-induced blackhole~\cite{xx}. If links D--A and X--C fail, X will hear announcements for $P_{g2}$ from D and will thus announce the $P_G$ externally. This announcement will bring to X traffic for $P_{g1}$ as well, but because of valley-free filtering, X does not have a valid route for $P_{g1}$ and will thus drop all traffic to it.

>>>>

 While configuring policies for a fully functional network is difficult, ensuring policy compliance in the face of failures can be almost impossible. Consider the data center network in Figure~\ref{fig:example2} with routers organized as a fat tree and running BGP.\footnote{For scale and policy flexibility, data center networks increasingly use BGP internally, with a private AS number per router~\cite{bgp-in-dc}.} The network has two clusters, one with services that should be reachable globally and one with services that should be accessible only internally. This policy is enabled by using non-overlapping address space in the two clusters and ensuring that only the address space for the global services is announced externally. Further, to reduce the number of prefixes that are announced externally, the global space is aggregated into a less-specific prefix \CD{PG}. The semantics of aggregation is that the aggregate prefix is announced as long as the router has a path to at least one sub-prefix.

The operator may decide that a simple way to implement the policy is to have X and Y: $i)$ not export externally what they hear from G and H, routers that belong to the local services cluster; and $ii)$ announce what they hear from routers C and D and aggregate to \CD{PG} if an announcement is subset of \CD{PG}. This implementation is appealing because X and Y do not need to be made aware of which prefixes are global versus local and IP address assignment can be done independently (e.g., new prefixes can be assigned to local services without updating router configurations).

However, this implementation does not have the right behavior in the face of failures. Suppose links X--G and X--H fail. Then, X will hear announcements for \CD{PL*} from C and D, having traversed from G and H to Y to C and D. Per policy implementation, X will start "leaking" these prefixes externally. Depending on the rationale for local services, this leak could impact security (e.g., if the services were sensitive) or availability (e.g., if the \CD{PL*} prefixes are used for other services outside of the data center). This problem does not manifest without failures because then X has and prefers paths to \CD{PL*} through G and H since they are shorter. A similar problem will happen if links Y--G and Y--H fail.
%\footnote{A different problem occurs when links X--C and X--D (or Y--C and Y--D) fail. X (Y) may stop announcing the global prefixes because they would be heard through G and H.}
Link failures in data centers are frequent and it is not uncommon to have multiple failed links at a given time~\cite{dc-failure-study}.

To avoid this problem, the operator may decide to disallow "valleys" paths, i.e., those that go up, down, and back up again. This guard can be implemented by $X$ and $Y$ rejecting paths through the other. But that creates a different problem in the face of failures---an aggregation-induced blackhole~\cite{xx}. If links D--A and X--C fail, X will hear announcements for \CD{PG2} from D and will thus announce the \CD{PG} externally. This announcement will bring to X traffic for \CD{PG1} as well, but because of valley-free filtering, X does not have a valid route for \CD{PG1} and will thus drop all traffic to it.

### 2016-01-28 paper/propane.tex
more edits

\begin{code}
\Define Routing = \{
     PCust \Path ExitCust \Prefer \End(Cust)
     PInt  \Path \End(\In)
     \True  \Path ExitCust \Prefer \Exit(Peer) \Prefer \Exit(Prov)
\}
\end{code}
\noindent
Line 2 of this policy 
defines the paths that exit our network to customer prefixes---\CD{ExitCust} defines paths through \CD{R1} and \CD{R2} and in the event
that connections to the customer through both of those routers fail,
a backup route (\CD{\End(Cust)}) is defined that admits traffic along
any path (including those through other networks) that ends at the customer.
Line 3 states that traffic for internal prefixes must end in our network, and is otherwise unconstrained.  The special keyword \In{} represents any location
inside the user's network whereas the keyword \Out{} represents any location
outside the user's network.
Line 4 applies to any other traffic, and allows any routes that leave through a peer with a preference for customers over peers over providers. To summarize our progress so far, the \CD{Routing} policy
implements (P1), (P3) and (P4) from Figure~\ref{fig:example1}.

Since routing allows transit traffic (\IE, traffic can enter from
\CD{Peer} and leave through \CD{Prov}), we should define a new policy that
implements this restriction separately.  We do so by using conjunction (\AND),
disjunction (\OR) and negation (\NOT) of constraints. 
%union (\Union), intersection (\Intersect), and negation (\NOT) to
%specify the appropriate sets of paths.
%
%% \begin{lstlisting}[mathescape=true]
%% define PP = Peer or Prov
%% define PPTransit = $enter(PP) \AND exit(PP)$
%% define CustTransit = $later(Cust) \AND later(Prov)$

%% define NoTransit = {
%%     $\path{true}{\neg PPTransit \AND \NOT CustTransit}$
%% }
%% \end{lstlisting}
\begin{code}
\Define PP = Peer \OR Prov
\Define PPTrans   = \Enter(PP) \OR \Exit(PP)
\Define CustTrans = \Later(Cust) \AND \Later(Prov)
\Define NoTrans   = \True \Path \NOT{}PPTrans \AND \NOT{}CustTrans
\end{code}
\noindent
The \CD{NoTrans} constraint above ensures that requirements (P2) and (P5) are satisfied. It says that for any prefix, traffic should never both enter and exit the network from \CD{Peer} or \CD{Prov}. Similarly it prevents traffic from ever following paths that leave our network and later passing through both \CD{Prov} and \CD{Cust}.  To implement both \CD{Routing}
and \CD{NoTrans} simultaneously, we simply conjoin them: \CD{Routing \AND{} NoTrans}.
%
%% \begin{lstlisting}[mathescape=true]
%% Routing $\AND$  NoTransit
%% \end{lstlisting}
%
These constraints capture the entire policy. From them, \sysname will generate per-device import and export filters, local preferences,
MED attributes, and community tags to ensure that the policy is
implemented correctly under all failure cases.

>>>>

\begin{code}
\Define Routing = \{
     PCust \Path ExitCust \Prefer \End(Cust)
     PInt  \Path \End(\In)
     \True  \Path ExitCust \Prefer \Exit(Peer) \Prefer \Exit(Prov)
\}
\end{code}
\noindent
Line 2 of this policy 
defines the paths that exit our network to customer prefixes---\CD{ExitCust} defines paths through \CD{R1} and \CD{R2}, and in the event
that connections to the customer through both routers fail,
a backup route (\CD{\End(Cust)}) is defined that admits traffic along
any path (including those through other networks) that ends at the customer.
Line 3 states that traffic for internal prefixes must end in our network, and is otherwise unconstrained.  The special keyword \In{} represents any location
inside the user's network and the keyword \Out{} represents any location
outside the user's network.
Line 4 applies to any other traffic, and allows any routes that leave through a peer with a preference for customers over peers over providers. To summarize our progress, the \CD{Routing} policy
implements (P1), (P3) and (P4) from Figure~\ref{fig:example1}.

Since routing allows transit traffic (\EG, traffic entering from
\CD{Peer} and leaving through \CD{Prov}), we define a new policy to implement this restriction separately, using conjunction (\AND),
disjunction (\OR) and negation (\NOT) of constraints. 
%union (\Union), intersection (\Intersect), and negation (\NOT) to
%specify the appropriate sets of paths.
%
%% \begin{lstlisting}[mathescape=true]
%% define PP = Peer or Prov
%% define PPTransit = $enter(PP) \AND exit(PP)$
%% define CustTransit = $later(Cust) \AND later(Prov)$

%% define NoTransit = {
%%     $\path{true}{\neg PPTransit \AND \NOT CustTransit}$
%% }
%% \end{lstlisting}
\begin{code}
\Define PP = Peer \OR Prov
\Define PPTrans   = \Enter(PP) \AND \Exit(PP)
\Define CustTrans = \Later(Cust) \AND \Later(Prov)
\Define NoTrans   = \{\True \Path \NOT{}PPTrans \AND \NOT{}CustTrans\}
\end{code}
\noindent
The \CD{NoTrans} constraint above ensures that requirements (P2) and (P5) are satisfied. It says that for any prefix, traffic should never both enter and exit the network from \CD{Peer} or \CD{Prov}. Similarly it prevents traffic from ever following paths that leave our network and later passing through both \CD{Prov} and \CD{Cust}.  To implement both \CD{Routing}
and \CD{NoTrans} simultaneously, we simply conjoin them: \CD{Routing \AND{} NoTrans}.
%
%% \begin{lstlisting}[mathescape=true]
%% Routing $\AND$  NoTransit
%% \end{lstlisting}
%
These constraints capture the entire policy. From them, \sysname will generate per-device import and export filters, local preferences,
MED attributes, and community tags to ensure that the policy is
implemented correctly under all failure cases.
